\bf\mftitle

### 2011-02-25 doc/jInfer/projecttype/projecttype.tex
#3187361 projecttype doc

\jmodule{ProjectType} is the module responsible for creation of NBP project type which groups input/output files that belongs to one specific inference. Each jInfer project also allows user to set properties specific for inference.\\

\begin{figure}
	\centering\includegraphics[scale=\myscale]{project_dir_structure}
	\caption{Project directory structure} \label{dir-structure}
\end{figure}

@@

Structure of \jmodule{ProjectType} can be divided into following five main parts.
\begin{itemize}
	\item Base classes - Classes providing main functionality like creation of project, defining operations like move, delete, copy etc. All the base classes are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype} package.
	\item Visualization classes - These classes create tree structure of project in NBP Projects view and are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype.nodes}
	\item Actions - Classes from \code{cz.cuni.mff.ksi.jinfer.projecttype.actions} package that provides actions allowing adding, removing input files into project, or running the project.
	\item Properties - Classes responsible for creation of project properties window with properties category tree. These are situated in  \code{cz.cuni.mff.ksi.jinfer.projecttype.properties} package.
	\item Project wizard - Classes representing creation of project through new project wizard from  \code{cz.cuni.mff.ksi.jinfer.projecttype.sample} package.
\end{itemize}

@@

\noindent Example of the structure follows.
\begin{verbatim}
	<?xml version="1.0" encoding="UTF-8" standalone="yes"?>
	<jinferinput>
	    <xml>
	        <file loc="/home/user/example.xml"/>
	    </xml>
	    <schemas>
	        <file loc="/home/user/example.dtd"/>
	    </schemas>
	    </queries/>
	</jinferinput>
\end{verbatim}

@@

Each project in NBP is after creation opened in project window and has some visual tree structure where each node in this tree is represented by NBP \code{Node} class. This structure is in jInfer project type provided by \code{JInferLogicalView} class that implements \code{LogicalViewProvider} interface from NBP and is available through \code{JInferProject} lookup. This class has one important method, \code{createLogicalView()} that returns instance of \code{RootNode} class of root node. Simple class structure is described in figure \ref{node-structure}.\\

@@

@@

Each jInfer project has associated properties window through which can user change project-wide properties. This window is accesible through \emph{properties} action in project \emph{root} node context menu. Properties window consists of category tree on a left side and properties pane on a right side. For each category in tree is associated one properties pane. Classes responsible for creation of this properties window are \code{JInferCustomizerProvider} and \code{JInferComponentProvider}.

>>>>

\jmodule{ProjectType} is the module representing a jInfer project in the NB platform, which groups input/output files that belongs to one specific inference. Each jInfer project also allows user to set properties specific for inference.\\

\begin{figure}
	\subfigure[Legend: Rectangle is folder, Rounded rectangle is file] {
		\centering\includegraphics[scale=\myscale]{project_dir_structure}
	}
	\caption{Project directory structure} \label{dir-structure}
\end{figure}

@@

Structure of \jmodule{ProjectType} can be divided into following five main parts.
\begin{itemize}
	\item Base classes - Classes providing main functionality like creation of project, defining operations like move, delete, copy etc. All the base classes are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype} package.
	\item Visualization classes - These classes create tree structure of project in NBP Projects view and are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype.nodes}.
	\item Actions - Classes from \code{cz.cuni.mff.ksi.jinfer.projecttype.actions} package that provides actions allowing adding, removing input files into project, or running the project.
	\item Properties - Classes responsible for creation of project properties window with properties category tree. These are situated in  \code{cz.cuni.mff.ksi.jinfer.projecttype.properties} package.
	\item Project wizard - Classes representing creation of project through new project wizard from  \code{cz.cuni.mff.ksi.jinfer.projecttype.sample} package.
\end{itemize}

@@

\noindent Example of the structure follows.
\begin{verbatim}
	<?xml version="1.0" encoding="UTF-8" standalone="yes"?>
	<jinferinput>
	    <xml>
	        <file loc="/home/user/example.xml"/>
	        <file loc="/home/user/example2.xml"/>
	    </xml>
	    <schemas>
	        <file loc="/home/user/example.dtd"/>
	    </schemas>
	    </queries/>
	</jinferinput>
\end{verbatim}

@@

Each jInfer project type in NBP is after creation opened in project window and has some visual tree structure where each node in this tree is represented by NBP \code{Node} class. This structure is in jInfer project type provided by \code{JInferLogicalView} class that implements \code{LogicalViewProvider} interface from NBP and is available through \code{JInferProject} lookup. This class has one important method, \code{createLogicalView()} that returns instance of \code{RootNode} class of root node. Simple class structure is described in figure \ref{node-structure}.\\

@@

TODO what kind of validation did we use. How to extend validation.\\

@@

Each jInfer project type has associated properties window through which can user change project-wide properties. This window is accesible through \emph{properties} action in project \emph{root} node context menu. Properties window consists of category tree on a left side and properties pane on a right side. For each category in tree is associated one properties pane. Category in a properties window is represented by NB platform \code{ProjectCustomizer.Category} class and properties pane is represented by \code{JPanel} class. Classes responsible for creation of this properties window are \code{JInferCustomizerProvider} and \code{JInferComponentProvider}.\\

\code{JInferComponentProvider} is very simple class that extends \code{ProjectCustomizer.CategoryComponentProvider} class from NBP and its only method is \code{create()} which takes category as a parameter and returns properties pane. In the \code{JInferCustomizerProvider} class, which extends NBP \code{CustomizerProvider} class, is the core functionality of collecting categories with associated properties panes from all jInfer modules. In section \ref{properties_reg} is described how to create your own category with associated properties pane, which will be present in jInfer project type properties window.\\

\subsubsection{Custom project properties}\label{properties_reg}
